A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-23 results.tex
rq2

Figure~\ref{fig:rq1} shows the final results. Although we found that our results were acceptable---the result reported by our embedding was top-4 as ranked by humans 88\% of the time---we investigated the other 12\% as well. We found that our embedding tended to fail in change patterns where the change involves many elements (e.g. adding a whole new \verb+impl+ block and implementing new functions in it). It is worth mentioning that these change patterns tend to apply across projects less often, as having many changed elements make it easier for datapoints to be dissimlar.

@@

We collected 60583 datapoints for general fix patterns using a server with a Xeon Gold 5120 processor (Q3-2017, 14-core 2.2 to 3.2GHz) and the data collection took around 26 hours to compute both $D_g$ and $D_b$. We used $\epsilon=0.0001$ and $Z=5$ as our DBSCAN parameters and that resulted in 577 clusters. After manual analysis, as described in~\ref{sec:manual_analysis_cluster_selection}, we ended up with 12 general patterns, which we describe in Table~\ref{table:general}. As shown in the table, we have separated the patterns based on the underlying program element (Category column). We have given each pattern a specific ID (ID column) and determined the number of instances manifesting that fix pattern (\# Instances column), as well as the number of projects in which the pattern was seen (\# Project column). Since these patterns are the general Rust patterns, it is worth mentioning that similar patterns can also be observed in other programming languages. To make this more clear, we will highlight these similarities in each pattern's description. We will also discuss the actionability of some of the patterns. Moreover, irrespective of their actionability, the empirical frequency numbers associated with each pattern can serve as valuable guidance for program repair tools. These frequency numbers provide insights into the importance and prevalence of the bugs, enabling repair tools to prioritize and address them accordingly. Now we provide a detailed description for each of these patterns:

>>>>

Figure~\ref{fig:rq1} shows the final results. Although we found that our results were acceptable---the result reported by our embedding was top-4 as ranked by humans 88\% of the time---we investigated the other 12\% as well. We found that our embedding tended to fail in change patterns where the change involves many elements (e.g. adding a whole new \verb+impl+ block and implementing new functions in it). Such failing change patterns tend to apply across projects less often, as having many changed elements make it easier for datapoints to be dissimlar.

@@

We collected 60583 datapoints for general fix patterns using a server with a Xeon Gold 5120 processor (Q3-2017, 14-core 2.2 to 3.2GHz) and the data collection took around 26 hours to compute both $D_g$ and $D_b$. We used $\epsilon=0.0001$ and $Z=5$ as our DBSCAN parameters, resulting in 577 clusters. After manual analysis, as described in~\ref{sec:manual_analysis_cluster_selection}, we ended up with 12 general patterns, which we describe in Table~\ref{table:general}. As shown in the table, we have separated the patterns based on the underlying program element (Category column). We have given each pattern a specific ID (ID column) and determined the number of instances manifesting that fix pattern (\# Instances column), as well as the number of projects in which the pattern was seen (\# Project column). Since these patterns are the general Rust patterns, analogous patterns can also occur in other programming languages, and we will discuss such patterns when describing each pattern. We will also discuss the actionability of some of the patterns. Moreover, no matter whether we can find actionable outcomes for the patterns, other researchers can use the empirical pattern frequency numbers that we report to build their own program repair tools, prioritizing more-frequently-repaired patterns. We next provide a detailed description of each of these patterns:
